A general framework for learning planning action models

### 2018-06-10 doc/aij18/background.tex
Background and Motivation completed
Background and Motivation completed

This section serves two purposes. In subsection \ref{basic_planning} we introduce the basic planning concepts as well as the classical planning model that we will use throughout the rest of the paper. Section \ref{related_work} summarizes existing approaches to learn action models in classical planning and highlights the novelty of our contribution via the related work.

%This section defines the planning model used on this work, {\em classical planning with conditional effects}, and the target of the learning/evaluation/recognition tasks addressed in the paper, a \strips\ action model.

@@

A {\em state} $s$ is a full assignment of values to fluents, i.e. $|s|=|F|$, so the size of the state space is $2^{|F|}$. Explicitly including negative literals $\neg f$ in states simplifies subsequent definitions but often, we will abuse notation by defining a state $s$ only in terms of the fluents that are true in $s$, as is common in \strips\ planning.

@@

\begin{itemize}
\item $\pre(a)\in\mathcal{L}(F)$, the {\em preconditions} of $a$, is the set of literals that must hold for the action $a\in A$ to be applicable.
\item $\eff^+(a)\in\mathcal{L}(F)$, the {\em positive effects} of $a$, is the set of literals that true after the application of the action $a\in A$.
\item $\eff^-(a)\in\mathcal{L}(F)$, the {\em negative effects} of $a$, is the set of literals that are false after the application of the action.
\end{itemize}

@@

A {\em classical planning problem} is a tuple $P=\tup{F,A,I,G}$, where $I$ is an initial state and $G\in\mathcal{L}(F)$ is a goal condition. A {\em plan} for $P$ is an action sequence $\pi=\tup{a_1, \ldots, a_n}$ that induces the {\em state trajectory} $s=\tup{s_0, s_1, \ldots, s_n}$ such that $s_0=I$ and, for each {\small $1\leq i\leq n$}, $a_i$ is applicable in $s_{i-1}$ and generates the successor state $s_i=\theta(s_{i-1},a_i)$. The {\em plan length} is denoted with $|\pi|=n$ . A plan $\pi$ {\em solves} $P$ iff $G\subseteq s_n$, i.e.~if the goal condition is satisfied at the last state reached after following the application of the plan $\pi$ in the initial state $I$.

In this work, we will use the term \emph{observation} to refer to the input knowledge of a learning task. Hence, $s=\tup{s_0, s_1, \ldots, s_n}$ is a fully-observable (\FO) state trajectory if every state $s_i$ is a full assignment of values to fluents and the minimal action sequence to transit from state $s_i$ to state $s_{i+1}$ is composed of a single action; that is, $\theta(s_i,\tup{a})=s_{i+1}$. Otherwise, $s$ is a partially-observable (\PO) state trajectory, meaning that at least one $s_i$ is a partial assignment of values to fluents in which one or more literals are missing. This general definition gives rise to two particular cases:

\begin{itemize}
\item when all fluents of a state $s_i$ are missing, $s_i$ is a \emph{missing} or \emph{empty} state
\item when the $n-1$ intermediate states of a trajectory $s$ are missing, $s$ is a \emph{non-observable} (\NO) state trajectory
\end{itemize}

Hence, a partially-observed state trajectory can be interpreted as a sequence that contains $n+1$ possibly incomplete states induced by an $n$-action sequence, or as a sequence with some missing intermediate states, which can be regarded as a particular case of partial observability. We will refer to the former as a \PO trajectory and to the latter as a \POstar state sequence.

%In the rest of the paper, we will use the following notation to refer to the different levels of state visibility: $s$ denotes a \FO state trajectory; $s^{+}$ refers to a \PO state trajectory with $n+1$ possibly incomplete states; $s^{*}$ indicates a \PO state trajectory with $m$ missing intermediate states, $m < n-1$; and $s^{0}$ is a \NO state trajectory with $n-1$ missing states.

Regarding an action sequence, $\tup{a_1, \ldots, a_n}$ is a \FO action sequence if it contains all the necessary actions to achieve the goal from an initial state, a \PO action sequence if at least one necessary action to achieve the goal is missing in the sequence and a \NO action sequence in case the sequence is empty.

A \emph{plan trace} is a combination of a state and an action sequence $\tau = \langle s_0, a_1, s_1, a_2, s_2, \ldots, a_n, s_n \rangle$. A plan trace $\tau$ for a planning problem $P=\tup{F,A,I,G}$ satisfies $s_0=I$, $G \in s_n$ and every element in the action sequence of $\tau$ is an action of $A$. Additionally, plan traces will be classified accordingly to the type of state trajectory (\FO, \PO, \POstar or \NO) and action sequence (\FO, \PO or \NO).

@@

The first column of Table \ref{table:models_comparison1} shows that all the approaches analyzed in this work accept partial observations of intermediate states, and some approaches also allow the sequence of intermediate states to be empty. Although not explicitly stated in the corresponding published works, it seems reasonable to assume that handling \NO state sequences subsumes \POstar trajectories and that a \POstar plan trace can be regarded as composed of several \NO sub-traces. Exceptionally, a \NO state sequence in \LOCM is a fully-empty trajectory, with neither initial or final state.

@@

The expressiveness of the learned action models varies across approaches (second column of Table \ref{table:models_comparison1}). All the presented systems are able to learn action models in a \textsc{Strips}  representation \cite{fikes1971strips} and some propose algorithms to learn more expressive action models that include quantifiers, logical implications or the type hierarchy of the domain.

@@

The \ARMS system became a benchmark in action-model learning, showing empirically that is is feasible lo learn a model in a reasonably efficient way using a weighted MAX-SAT even with \NO state trajectories. Nevertheless, we argue that using the home-made error and redundancy metrics to evaluate the model correctness is questionable since a model that exhibits a wrong precondition or effect in any of its actions could still be eligible as the minimal-error output model.

\begin{table}
	\small
	\centering
	\begin{tabular}{ l | c | c | c }
		& \multicolumn{1}{c}{Input plan traces}
        & \multicolumn{1}{c}{Learned action model}
        & \multicolumn{1}{c}{Technique}     \\
		\hline			
		\multirow{2}{*}{\ARMS} & \PO and \NO states & \strips & MAX-SAT \\ & \FO actions & & \\
        \hline
        \multirow{2}{*}{\SLAF} & \PO states  & universal quantifiers in $\eff$ & logical inference \\ & \FO actions &  & SAT solver \\
         \hline
        %\multirow{2}{*}{\SLAF} & PO states and FO actions & existential quantifiers in $\pre$ \\ & & universal quantifiers in $\eff$ &  bayesian learning \\ & & & logical filtering \\
         %\hline
		\multirow{2}{*}{\LAMP} & \PO and \PO* states &  quantifiers &  Markov logic networks \\  & \FO actions & logical implications &  \\
         \hline
         \AMAN & \NO states & \strips & graphical model estimation \\ & noisy actions & & \\
         \hline
         \NOISTA & \PO and noisy states & \strips &  classification \\ & \FO actions & & \strips \texttt{} rules derivation \\
         \hline
         \CAMA & \PO and \PO* states &  \strips & crowdsourcing annotation\\ & \FO actions &  & MAX-SAT \\
         \hline
         \LOCMtwo & \NO states &  predicates and types & Finite State Machines \\ & \FO actions & & \\
         \hline
		\FAMA &  \PO, \PO* and \NO states & \strips &   compilation to planning\\ & \PO and \NO actions & & \\
         \hline
	\end{tabular}
	\caption{Characteristics of action-model learning approaches}
	\label{table:models_comparison1}
\end{table}

A tractable and exact solution of action models in partially observable domains using a technique known as Simultaneous Learning and Filtering (\textbf{\SLAF}) is presented in~\cite{AmirC08}. \SLAF alongside \ARMS can be considered another of the precursors of the modern algorithms for action-model learning, able to learn from plan traces with PO and non-null intermediate states. Given a formula representing the initial belief state, a sequence of executed actions and the corresponding partially observed states, \SLAF builds a complete explanation of observations by models of actions through a CNF formula. The learning algorithm updates the formula of the belief state with every action and observation in the sequence such that the new transition belief formula represents all possible transition relations consistent with the actions and observations at every time step.

@@

\LAMP allows \POstar state observations up to a minimum percentage of 1/5 of the observed states as well as \PO state trajectories with different degrees of observability in the number of propositions in each state. It uses an error metric based on counting the differences in the number of precondition and effects between the ground-truth model and the learned model. In general, the results show that the accuracy of the learned models is fairly sensitive to the threshold chosen to learn the weights of the candidate formulas, and that domains that feature more conditional effects are harder to learn.

@@

The Action Model Acquisition from Noisy plan traces (\textbf{\AMAN}) \cite{zhuo2013action} introduces an algorithm able to learn action models from plan traces with \NO state sequences where actions have a probability of being observed incorrectly (noisy actions). The first step of the \AMAN algorithm is to build the set of candidate domain models that are compliant with the action headers and predicates. \AMAN then builds a graphical model to capture the domain physics; i.e., the relations between states, correct actions, observed actions and domain models. After that, the parameters of the graphical model are learned, computing at the same time the probability distribution of each candidate domain model. Finally \AMAN returns the model that maximizes a reward function defined in terms of the percentage of actions successfully executed and the percentage of goal propositions achieved after the last successfully executed action.

\AMAN uses the same metric as \LAMP, namely counting the number of preconditions and effects that appear in the learned model and not in the ground-truth model (extra fluents) and viceversa (missing fluents). In a comparison between \AMAN and \ARMS on noiseless inputs, the results show that the accuracies of both \AMAN and \ARMS are very close to each other and neither dominates the other. On the other hand, a test comparing plan traces with and without noisy actions reveals that the accuracy in the case \emph{with noise} becomes more and more close to \emph{without noise} as the number of iterations of \AMAN algorithm increases because the distribution of noise in the plan becomes gradually closer to the real distribution.

@@

The Crowdsourced Action-Model Acquisition (\textbf{\CAMA}) \cite{Zhuo15} explores knowledge from both crowdsourcing (human annotators) and plan traces to learn action models for planning. \CAMA relies on the assumption that obtaining enough training samples is often difficult and costly because there is usually a limited number of plan traces available. In order to overcome this limitation, \CAMA builds on a set of soft constraints based on labels \texttt{true} or \texttt{false} given by the crowd and a set of soft constraints based on the input plan traces. Then it solves the constraint-based problem using a MAX-SAT solver and converts the solution to action models. An experimental comparison reveals that a manual crowdsourcing of \CAMA outperforms \ARMS and that as expectedly the difference becomes smaller as the number of plan traces becomes larger. The accuracy of \CAMA for a small number of plan traces (e.g., 30) is not less than 80\%, which means that exploiting the knowledge of the crowd can help learning action models.

@@

The Learning Object-Centred Models (\textbf{\LOCM}) is an approach that only requires the \FO action sequence as input knowledge, without need for providing any information about the predicates or the state trajectory, not even the initial or final state~cite{cresswell2013acquiring}. The lack of available information is overcome by exploiting assumptions about the structure of the actions. Particularly, it assumes that objects found in the same position in the header of actions are grouped as a collection of objects (sorts) whose defined set of states is captured by a parameterized Finite State Machine (FSM). The intuitive assumptions of \LOCM, like the continuity of object transitions or the association of parameters between consecutive actions in the training datset, yield a learning model heavily reliant on the kind of domain structure. A later work, \textbf{\LOCMtwo}, extends the applicability of the \LOCM algorithm to a wider range of domains by introducing a richer representation that allows using multiple FSMs to represent the state of a sort~\cite{cresswell2011generalised}.

\LOCMtwo is not experimentally evaluated and only the outcome of running the \LOCMtwo algorithm on several benchmark domains wrt to the reference model is reported. It is worth noting the last contribution of \LOCM, called \textbf{\LOP} (\LOCM with Optimized Plans), addresses the problem of inducing static predicates~\cite{GregoryC16}. \LOP applies a post-processing step after the \LOCM analysis and it requires additional input information, particularly a set of optimal plans besides the suboptimal \FO action sequences.

>>>>

This section serves two purposes: first we introduce the basic planning concepts as well as the classical planning model that we will use throughout the rest of the paper; and secondly, we summarize the existing approaches to learn action models in classical planning and highlight our contributions via the related work.

@@

A {\em state} $s$ is a full assignment of values to fluents, i.e. $|s|=|F|$, so the size of the state space is $2^{|F|}$. Explicitly including negative literals $\neg f$ in states simplifies subsequent definitions but often, we will abuse notation by defining a state $s$ only in terms of the fluents that are true in $s$, as it is common in \strips\ planning.

@@

\begin{itemize}
\item $\pre(a)\in\mathcal{L}(F)$, the {\em preconditions} of $a$, is the set of literals that must hold for the action $a\in A$ to be applicable.
\item $\eff^+(a)\in\mathcal{L}(F)$, the {\em positive effects} of $a$, is the set of literals that are true after the application of the action $a\in A$.
\item $\eff^-(a)\in\mathcal{L}(F)$, the {\em negative effects} of $a$, is the set of literals that are false after the application of the action.
\end{itemize}

@@

A {\em classical planning problem} is a tuple $P=\tup{F,A,I,G}$, where $I$ is an initial state and $G\in\mathcal{L}(F)$ is a goal condition. A {\em plan} for $P$ is an action sequence $\pi=\tup{a_1, \ldots, a_n}$ that induces the {\em state trajectory} $s=\tup{s_0, s_1, \ldots, s_n}$ such that $s_0=I$ and, for each {\small $1\leq i\leq n$}, $a_i$ is applicable in $s_{i-1}$ and generates the successor state $s_i=\theta(s_{i-1},a_i)$. The {\em plan length} is denoted with $|\pi|=n$ . A plan $\pi$ {\em solves} $P$ iff $G\subseteq s_n$, i.e.,~if the goal condition is satisfied at the last state reached after following the application of the plan $\pi$ in the initial state $I$. A solution plan is {\em optimal} if it has minimum length.

In this work, the term \emph{plan trace} refers to the \emph{observation} of a plan execution that starts on a given initial state, which constitutes the input knowledge of a learning task. Specifically, $s=\tup{s_0, s_1, \ldots, s_n}$ is a fully-observable (\FO) state trajectory if every state $s_i$ is a full assignment of values to fluents and the minimal action sequence to transit from state $s_i$ to state $s_{i+1}$ is composed of a single action; that is, $\theta(s_i,\tup{a})=s_{i+1}$. Otherwise, $s$ is a partially-observable (\PO) state trajectory, meaning that at least one $s_i$ is a partial assignment of values to fluents in which one or more literals are missing. This implies that all fluents of a state $s_i$ may be missing, in which case, $s_i$ is a \emph{missing} or \emph{empty} state. This general definition of \PO gives rise to two particular cases:

\begin{itemize}
\item when \textbf{all} the $n-1$ intermediate states of a trajectory $s$ are \textbf{missing}, $s$ is a \emph{non-observable} (\NO) state trajectory
\item when \textbf{none} of the $n-1$ intermediate states of a trajectory $s$ is \textbf{missing}, we will refer to $s$ as a \POstar state trajectory
\end{itemize}

Table \ref{tab:state_trajectory} summarizes the four types of state trajectories according to the observed information, which ultimately affects the number of observed intermediate states and the number of literals comprised in each intermediate state. \PO comprises both \POstar and \NO, and it thus encompasses trajectories with some missing state.

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c|}
	     & \# intermediate states & state type \\ \hline
	\FO & $n-1$  & {\small $\forall i, 1 \leq i < n$}  \\  & & $s_i$ is a full assignment \\ \hline
    \multirow{1}{*}{\POstar} & $n-1$ & {\small $\exists i, 1 \leq i < n$}  \\ & & $s_i$ is a partial assignment \\ \hline
    \multirow{1}{*}{\PO} & $\leq n-1$ & {\small $\exists i, 1 \leq i < n$}   \\  & & $s_i$ is a partial assignment \\ \hline
    \NO & 0  & ---  \\ \hline
\end{tabular}
\caption{Classification of state trajectories accordingly to observation}
\label{tab:state_trajectory}
\end{table}

Regarding an action sequence, $\tup{a_1, \ldots, a_n}$ is a \FO action sequence if it contains all the necessary actions to transit every state $s_{i-1}$ to the corresponding successor state $s_{i}$, for each {\small $1\leq i\le n$}. We say it is a \PO action sequence if at least one of these necessary actions is missing in the sequence and a \NO action sequence in case the sequence is empty.

A \emph{plan trace} $\tau$ is a combination of a state and an action sequence: $\tau = \langle s_0, a_1, s_1, a_2, s_2, \ldots, a_n, s_n \rangle$. A plan trace $\tau$ for a planning problem $P=\tup{F,A,I,G}$ satisfies $s_0=I$, $G \in s_n$ and every element in the action sequence of $\tau$ is an action of $A$. Additionally, plan traces will be classified accordingly to the type of state trajectory (\FO, \POstar, \PO or \NO) and action sequence (\FO, \PO or \NO).

@@

The first column of Table \ref{table:models_comparison1} shows the constraints imposed on the input plan traces with regards to observability. Since all approaches except ours deal only with \FO action sequences, constraints are exclusively concerned with the type of state trajectory. This directly affects the complexity of the task, which can be sorted from the least to the most constrained following this order: 1) \NO, 2) \PO, 3) \POstar, and 4) \FO. Note that \PO is less constrained than \POstar because it also includes the possibility of having some missing state in the trajectory.

The task of learning from less constrained traces subsumes learning from more constrained ones. Consequently, approaches to learning from, for instance, traces with \PO state trajectories will also be able to learn from traces with \POstar state trajectories. All the approaches analyzed in this work accept the more constrained definition of partial observations of intermediate states \POstar, and most of them also allow the sequence of intermediate states to be empty. Exceptionally, a \NO state sequence in \LOCM is a fully-empty trajectory, with neither initial or final state.

@@

The expressiveness of the learned action models varies across approaches (second column of Table \ref{table:models_comparison1}). All the presented systems are able to learn action models in a \textsc{Strips}  representation \cite{fikes1971strips} and some propose algorithms to learn more expressive action models that include quantifiers, logical implications or the type hierarchy of a PDDL domain.

@@

The \ARMS system became a benchmark in action-model learning, showing empirically that is is feasible lo learn a model in a reasonably efficient way using a weighted MAX-SAT even with \NO state trajectories.
%Nevertheless, we argue that using the home-made error and redundancy metrics to evaluate the model correctness is questionable since a model that exhibits a wrong precondition or effect in any of its actions could still be eligible as the minimal-error output model.

\begin{table}
	\small
	\centering
	\begin{tabular}{ l | c | c | c }
		& \multicolumn{1}{c}{Input plan traces}
        & \multicolumn{1}{c}{Learned action model}
        & \multicolumn{1}{c}{Technique}     \\
		\hline			
		\multirow{2}{*}{\ARMS} & \NO states & \strips & MAX-SAT \\ & \FO actions & & \\
        \hline
        \multirow{2}{*}{\SLAF} & \POstar states  & universal quantifiers in $\eff$ & logical inference \\ & \FO actions &  & SAT solver \\
         \hline
        %\multirow{2}{*}{\SLAF} & PO states and FO actions & existential quantifiers in $\pre$ \\ & & universal quantifiers in $\eff$ &  bayesian learning \\ & & & logical filtering \\
         %\hline
		\multirow{2}{*}{\LAMP} & \PO states &  quantifiers &  Markov logic networks \\  & \FO actions & logical implications &  \\
         \hline
         \AMAN & \NO states & \strips & graphical model estimation \\ & noisy actions & & \\
         \hline
         \NOISTA & \POstar and noisy states & \strips &  classification \\ & \FO actions & & \strips \texttt{} rules derivation \\
         \hline
         \CAMA & \PO states &  \strips & crowdsourcing annotation\\ & \FO actions &  & MAX-SAT \\
         \hline
         \LOCMtwo & \NO states &  predicates and types & Finite State Machines \\ & \FO actions & & \\
         \hline
		\FAMA & \NO states & \strips &   compilation to planning\\ & \NO actions & & \\
         \hline
	\end{tabular}
	\caption{Characteristics of action-model learning approaches}
	\label{table:models_comparison1}
\end{table}

A tractable and exact solution of action models in partially observable domains using a technique known as Simultaneous Learning and Filtering (\textbf{\SLAF}) is presented in~\cite{AmirC08}. \SLAF alongside \ARMS can be considered another of the precursors of the modern algorithms for action-model learning, able to learn from partially observable states. Given a formula representing the initial belief state, a sequence of executed actions and the corresponding partially observed states, \SLAF builds a complete explanation of observations by models of actions through a CNF formula. The learning algorithm updates the formula of the belief state with every action and observation in the sequence such that the new transition belief formula represents all possible transition relations consistent with the actions and observations at every time step.

@@

\LAMP allows \PO state trajectories up to a minimum percentage of 1/5 of non-empty states as well as \POstar state trajectories with different degrees of observability in the number of propositions in each state. It uses an error metric based on counting the differences in the number of precondition and effects between the ground-truth model and the learned model. In general, the results show that the accuracy of the learned models is fairly sensitive to the threshold chosen to learn the weights of the candidate formulas, and that domains that feature more conditional effects are harder to learn.

@@

The Action Model Acquisition from Noisy plan traces (\textbf{\AMAN}) \cite{zhuo2013action} introduces an algorithm able to learn action models from plan traces with \NO state sequences where actions have a probability of being observed incorrectly (noisy actions). The first step of the \AMAN algorithm is to build the set of candidate domain models that are compliant with the action headers and predicates. \AMAN then builds a graphical model to capture the domain physics; i.e., the relations between states, correct actions, observed actions and domain models. After that, the parameters of the graphical model are learned, computing at the same time the probability distribution of each candidate domain model. \AMAN finally returns the model that maximizes a reward function defined in terms of the percentage of actions successfully executed and the percentage of goal propositions achieved after the last successfully executed action.

\AMAN uses the same metric as \LAMP, namely counting the number of preconditions and effects that appear in the learned model and not in the ground-truth model (extra fluents) and viceversa (missing fluents). In a comparison between \AMAN and \ARMS on noiseless inputs, the results show that the accuracies of both \AMAN and \ARMS are very close to each other and neither dominates the other. The convergence property of \AMAN guarantees that the accuracy of the learned model with noisy input traces becomes more and more close to the case  \emph{without noise} because the distribution of noise in the plan becomes gradually closer to real distribution with the number of iterations.

%On the other hand, a test comparing plan traces with and without noisy actions reveals that the accuracy in the case \emph{with noise} becomes more and more close to \emph{without noise} as the number of iterations of \AMAN algorithm increases because the distribution of noise in the plan becomes gradually closer to the real distribution.

@@

The Crowdsourced Action-Model Acquisition (\textbf{\CAMA}) \cite{Zhuo15} explores knowledge from both crowdsourcing (human annotators) and plan traces to learn action models for planning. \CAMA relies on the assumption that obtaining enough training samples is often difficult and costly because there is usually a limited number of plan traces available. In order to overcome this limitation, \CAMA builds on a set of soft constraints based on labels \texttt{true} or \texttt{false} given by the crowd and a set of soft constraints based on the input plan traces. Then it solves the constraint-based problem using a MAX-SAT solver and converts the solution to action models.

Plan traces in \CAMA are composed of 80\% of empty states and each partial state was selected by 50\% of propositions in the corresponding full state. An experimental comparison reveals that a manual crowdsourcing of \CAMA outperforms \ARMS and that as expectedly the difference becomes smaller as the number of plan traces becomes larger. The accuracy of \CAMA for a small number of plan traces (e.g., 30) is not less than 80\%, thus revealing that exploiting the knowledge of the crowd can help learning action models.

@@

The Learning Object-Centred Models (\textbf{\LOCM}) is an approach that only requires the \FO action sequence as input knowledge, without need for providing any information about the predicates or the state trajectory, not even the initial or final state~\cite{CresswellMW09,cresswell2013acquiring}. The lack of available state information is overcome by exploiting assumptions about the structure of the actions. Particularly, \LOCM assumes that objects found in the same position in the header of actions are grouped as a collection of objects (sorts) whose defined set of states is captured by a parameterized Finite State Machine (FSM). The intuitive assumptions of \LOCM, like the continuity of object transitions or the association of parameters between consecutive actions in the training dataset, yield a learning model heavily reliant on the kind of domain structure. A later work, \textbf{\LOCMtwo}, extends the applicability of the \LOCM algorithm to a wider range of domains by introducing a richer representation that allows using multiple FSMs to represent the state of a sort~\cite{cresswell2011generalised}.

\LOCMtwo is not experimentally evaluated, only the outcome of running the \LOCMtwo algorithm on several benchmark domains wrt to the reference model is reported in ~\cite{cresswell2011generalised}. It is worth noting the last contribution of the \LOCM family, called \textbf{\LOP} (\LOCM with Optimized Plans), addresses the problem of inducing static predicates~\cite{GregoryC16}. \LOP applies a post-processing step after the \LOCM analysis and it requires additional input information, particularly a set of optimal plans besides the suboptimal \FO action sequences.
